Measuring Hash Trustworthiness via Collision Utility Metrics: Logical Cryptanalysis of MD4

### 2017-11-29 dsn-2018/bare_conf.tex
Extend new collisions sections
Signed-off-by: Alexander Scheel <alexander.m.scheel@gmail.com>

Through the exploration of the neighborhood technique, we have found over
35,000 new differential paths which originated from the five original
collisions in MD4. This shows that the neighborhood definition is sufficient
to produce a large quantity of new collision classes.

@@

\textbf{TODO} - Discuss impacts on real-world systems like MD5, SHA-1, etc.

>>>>

Through the exploration of the neighborhood technique, we have found over
35,000 new differential paths which originated from the five original
collisions in MD4. This shows that the neighborhood definition is sufficient
to produce a large quantity of new collision classes. Further, we give
evidence for propagating neighborhoods across reduced round versions of MD4,
and show a new collision in MD4 with new differential path.

\subsection{Extensions of Prior Work}

We noted in table \ref{table:neighborhood} that the unit-step neighborhood of
the existing attacks were non-empty. By repeatedly expanding neighborhoods of
known collision classes, we can construct paths in the collision space. We
made the following observations:

\begin{enumerate}
    \item The space of collision classes is not smooth under the unit distance
        relation. That is, starting at $C_{Schlaffer}$ and evaluating
        successive neighborhoods, moving towards $C_{Wang}$ whenever the
        distance decreases does not lead to a simple path of length
        $\delta(C_{Schlaffer}, C_{Wang}) = 17$. Our lower bound on the actual
        distance is 29, but after 14 rounds of expansion, we only reduced the
        distance to 15.
    \item Even under successive unit neighborhoods, the family of input block
        differentials remains roughly the same among. This can be partially
        counteracted by moving to reduced-round spaces, evaluating the
        neighborhood, and expanding back to a collision in full-round MD4.
        That is, there is a detectable signature of sharing significant
        input block differential structure with the original collision.
        With 35,918 unique classes of collisions which had 176 unique
        families of collisions, there were only three unique families of
        input block differentials: those of the starting collision classes.
\end{enumerate}

This last point show that, while there may be a number of unique differentials
for a given collision class, and potentially many collision classes within
some neighborhood of the original collision class, by analyzing the structure
of the input block differential, systems can potentially prohibit successful
collision attacks by preventing structures of input block differences.

\textbf{TODO - figures and graphics on dataset}

\subsection{New Differentials}

We present the following new differentials as part of our work:

\textbf{TODO - figures and graphics on new differentials/differential paths}

@@

\textbf{TODO} - Recap impacts on real-world systems like MD5, SHA-1, etc.
